Workflow Part II: Inverse root modeling and post-processing

### 2021-03-16 Readme.Rmd

Set-up and run effective rooting depth models, evaluate model, and join ERD from the predicted model with hydraulic traits and mortality data, and calcualted realized hydraulic risk

@@

**Figures**

```{r Chunk 08.0, eval = FALSE}
source("code/06.0_load.R")
source("code/08.0_manuscript_data_figs.R")
```

**Main text**

```{r Chunk 09.0, eval = FALSE}
render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
```

@@

>>>>

Set-up and run effective rooting depth models, evaluate model, and join ERD from the predicted model with hydraulic traits and mortality data, and calculated realized hydraulic risk

@@

**Main text**
```{r Chunk 09.0, eval = FALSE}
# Two files are used within the report
# For data, 06.0_load.R and 
# For figures and data, code/08.0_manuscript_data_figs.R
if (!require("groundhog")) install.packages("groundhog"); 
groundhog.folder <- paste0("Users/ftuser/Library/R/4.0/library/bci.roots.inversion")
if(!dir.exists(file.path(groundhog.folder))) {dir.create(file.path(groundhog.folder))}
set.groundhog.folder(groundhog.folder)
library(groundhog)
groundhog.day = "2021-01-01"
groundhog.library('rmarkdown', groundhog.day)
groundhog.library('bookdown', groundhog.day)
rmarkdown::render("09.0_manuscript.rmd", output_format = "bookdown::html_document2")
```

@@

```{r Chunk 11.0, eval = FALSE}
remotes::install_github("ropenscilabs/reviewer")
modified_file <- system.file("extdata/CheatSheet-modified.Rmd", package = "reviewer")
reference_file <- system.file("extdata/CheatSheet.Rmd", package = "reviewer")
library(reviewer)
result <- diff_rmd(modified_file, reference_file)
groundhog.library('diffobj', groundhog.day)
browseVignettes("diffobj")
remotes::install_github("ropenscilabs/trackmd")
trackmd::trackChanges("09.0_manuscript.rmd")
```
<!-- groundhog.library('diffr', groundhog.day) -->
<!-- diffr("09.0_manuscript_NP1.rmd", "09.0_manuscript.rmd") -->
